\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.5in]{geometry}
\usepackage{lmodern}
\usepackage{nopageno}
\usepackage{indentfirst}

\titleformat{\section}
{\LARGE}
{}
{0pt}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0pt}
{}

\titlespacing*{\section}{0pt}{0pt}{0.1in}
\titlespacing*{\subsection}{0pt}{0pt}{0in}

\renewcommand{\maketitle}
{
\begin{flushleft}
\huge
\textbf{\theauthor}
\small

brandonhawi@jasonbusiness.com

www.github.com/brandonhawi

(818) 855 - 0542
\end{flushleft}
}

%\renewcommand{\familydefault}{cmvtt}

\begin{document}

\title{R\'esum\'e}
\author{Brandon Hawi}

\maketitle
\vspace{-0.1in}
\section{Education}

\subsection{University of California, Irvine (March 2020)}
\noindent\textit{B.S., Computer Science and Engineering}

\subsection{College of the Canyons (June 2016)}
\noindent\textit{A.S., Mathematics}

Obtained an Associate of Science Degree in Mathematics with honors while concurrently attending
high school.

\section{Professional Experience}

%\subsection{Target}
%
%Team Member
%
%Worked as a cashier at Target in the Tustin Marketplace.
%

\subsection{SkyWorks Solutions (June - Present)}

\noindent\textit{Software Intern (Wafer Foundry Engineering)}

Working as a software intern at the Wafer Foundry Engineering Group at SkyWorks Solutions to 
analyze data, develop scripts for automation, and maintain the in-house website for the group.

\subsection{Axxiom Data, Inc. (May - September 2017)}

\noindent\textit{Software Intern}

Worked directly under the CEO of Axxiom Data to help develop new solutions within Axxiom's
content management system, upkeep it's current websites, and prepare the system for future development.

\subsection{Invisible Touch Events (January - September 2017)} 

\noindent\textit{Light/Audio Technician}

Worked as a technician for an event planning company based in the Tustin area and helped research
new lighting/audio solutions for events, troubleshoot electrical issues on the fly, and develop 
connections with clients to maintain future business.

\section{Projects}

\subsection{SystemVerilog RISC-V Processor (2019)}

Designed a 5-stage pipelined processor in SystemVerilog utilizing SystemVerilog interfaces and other 
SystemVerilog programming features. After designing the processor, I reworked parts of the processor 
to be synthesizable; the synthesis ran at a clock speed of 3.8 ns (~260 MHz).

\subsection{Python SoundCloud Scraper (2019)}

Wrote a Python script that scraped SoundCloud's website and checked specific artists' profiles occasionally for new music uploads. 
I would manually update the list of artists and the script would send me a text using an API called Twilio.

\subsection{Pure Lisp Interpreter (2019)}

Wrote the evaluation function for Pure Lisp using Pure Lisp. This required recursion and the use of a global 
association list to create the functionality of dynamic typing that is used in Lisp and many scripting languages today.

\subsection{EthicsViz (2018)}

Worked with a researcher on the University of California, Irvine campus to develop a system that analyzed 
user's online data using platforms such as Google History, Spotify, and Google Maps. The system's goal was to present interesting correlations using users' online "footprint".  

\subsection{Discrete Cosine Transform VHDL (2018)}

Designed and simulated a Discrete Cosine Transform circuit using VHDL and Xilinx. The chip was designed to be 
used for video compression. 

\section{Other Experience}

\subsection{Engineering Conference UCI}

\noindent\textit{Project Manager, Design Lead}

Led a team in researching and compiling a 41 page research report detailing the implementation of an 
autonomous vertical farm that utilized an evolutionary algorithm and a convolutional neural network 
to improve biomass yield every iteration. The research report was published by the University of 
California, Irvine and can be found on their eScholarship website.

\subsection{Kappa Sigma Fraternity}

\noindent\textit{Treasurer, Website Designer, Recruitment Chair}

Organized biannual recruitment for three years, managed a yearly \$80,000 yearly budget, and designed 
the chapter's website.

\section{Relevant Coursework}

\begin{itemize}
	\item[$-$] Three courses (one year) of Python coursework
	\item[$-$] Three courses (one year) utilizing Unix server scripting
	\item[$-$] One course in Databases utilizing SQL
	\item[$-$] One semester of Proficiency in Microsoft Programs using VBA
\end{itemize}

\section{Technical Skills}

\subsection{Languages}

C, C++, Java, SQL, HTML, CSS, JavaScript, VBA, Lisp, Prolog, Python, \LaTeX

\subsection{Tools}

Unix, Linux, Xilinx, VHDL, MATLAB, Mathematica

\end{document}
