\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.5in]{geometry}
\usepackage{lmodern}
\usepackage{nopageno}
\usepackage{indentfirst}
\usepackage{enumitem}

\setlist{nosep}

\titleformat{\section}
{\centering\LARGE\bfseries}
{}
{0pt}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0pt}
{}

\titlespacing*{\section}{0pt}{0pt}{0.1in}
\titlespacing*{\subsection}{0pt}{0pt}{0in}

\renewcommand{\maketitle}
{
\begin{flushleft}
\huge
\textbf{\theauthor}
\small

brandonhawi@jasonbusiness.com

www.github.com/brandonhawi

(818) 855 - 0542
\end{flushleft}
}

%\renewcommand{\familydefault}{cmvtt}

\begin{document}

\title{R\'esum\'e}
\author{Brandon Hawi}

\maketitle
\vspace{-0.1in}
\section{Education}

\subsection{University of California, Irvine (March 2020)}
\noindent\textit{B.S., Computer Science and Engineering}

\subsection{College of the Canyons (June 2016)}
\noindent\textit{A.S., Mathematics}

Obtained an Associate of Science Degree in Mathematics with honors while concurrently attending
high school.

\section{Professional Experience}

%\subsection{Target}
%
%Team Member
%
%Worked as a cashier at Target in the Tustin Marketplace.
%

\subsection{Skyworks Solutions (June - Present)}

\noindent\textit{Software Engineer Intern (Wafer Foundry Engineering)}
\begin{itemize}
	\setlength\itemsep{0em}
	\item Developing custom automation solutions to decrease cycle time of tapeout production
	\item Maintaining a full stack web application that uses ASP.NET and C\# as a front end and Microsoft SQL Express and Python as a back end
	\item Wrote a shell script automation that improved design efficiency by 80\%
\end{itemize}

\subsection{Axxiom Data, Inc. (May - September 2017)}

\noindent\textit{Software Intern}
\begin{itemize}
	\setlength\itemsep{0em}
	\item Developed new features for Axxiom's content management system using PHP
	\item Implemented an automation solution using Python to make the product creation process 180 times faster
	\item Introduced the Git VCS to Axxiom and improved development time by leveraging its use
\end{itemize}

\section{Projects}

\subsection{Python SoundCloud Scraper (2019)}

Wrote a Python script that scraped SoundCloud's website and checked specific artists' profiles occasionally for new music uploads. 
I would manually update the list of artists and the script would send me a text using an API called Twilio.

\subsection{Pure Lisp Interpreter (2019)}

Wrote the evaluation function for Pure Lisp using Pure Lisp. This required recursion and the use of a global 
association list to create the functionality of dynamic typing that is used in Lisp and many scripting languages today.

\subsection{EthicsViz (2018)}

Worked with a researcher on the University of California, Irvine campus to develop a system that analyzed 
user's online data using platforms such as Google History, Spotify, and Google Maps. The system's goal was to present interesting correlations using users' online "footprint".  The system used D3.js, a JavaScript library for data-driven documents. 

\section{Other Experience}

\subsection{Engineering Conference UCI}

\noindent\textit{Project Manager, Design Lead}

Led a team in researching and compiling a 41 page research report detailing the implementation of an 
autonomous vertical farm that utilized an evolutionary algorithm and a convolutional neural network 
to improve biomass yield every iteration. The research report was published by the University of 
California, Irvine and can be found on their eScholarship website.

\subsection{Kappa Sigma Fraternity}

\noindent\textit{Treasurer, Website Designer, Recruitment Chair}

Organized biannual recruitment for three years, managed a yearly \$150,000 yearly budget, and designed 
the chapter's website using HTML, CSS, and JavaScript.

\section{Technical Skills}

\subsection{Languages}

 JavaScript, Node.js, Python, C, C++, C\#, Java, SQL, HTML, CSS, \LaTeX

\subsection{Tools}

Unix, Linux, Xilinx, VHDL, MATLAB, Mathematica, ASP.NET

\end{document}
